---
title: acewater
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![license](https://img.shields.io/github/license/mashape/apistatus.svg)]()

acewater provides an interface to the [US Army Corps of Engineers' water monitoring data along the Lake Washington Ship Canal](http://www.nwd-wc.usace.army.mil/nws/hh/www/index.html).
The main function, `get_water_conditions` returns a tidy data frame (a [tibble](http://tibble.tidyverse.org)).

## Installation

You can install acewater from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("briandconnelly/acewater")
```

## Example

### Get the most recent conditions at the Fremont Bridge (station FBLW)

```{r example}
library(acewater)
library(magrittr)

get_water_conditions("FBLW")
```

## Contributer Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.

