---
title: acewater
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![license](https://img.shields.io/github/license/mashape/apistatus.svg)]()

acewater provides an interface to the real-time water monitoring data provided by the [Water Management Section of the Seattle District Corps of Engineers](http://www.nwd-wc.usace.army.mil/nws/hh/www/index.html), which covers most of Washington, Northern Idaho, and Northwestern Montana.
The main function, `get_water_conditions` returns a tidy data frame (a [tibble](http://tibble.tidyverse.org)).


## Installation

You can install acewater from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("briandconnelly/acewater")
```

## Example

### Get the current conditions at the [Grand Coulee Dam](https://en.wikipedia.org/wiki/Grand_Coulee_Dam) (GCL), part of the [Eastern Washington Rivers](http://www.nwd-wc.usace.army.mil/nws/hh/www/eastern.html) (EWA) project:

```{r Eaxmple Grand Coulee Dam}
library(acewater)

get_water_conditions(station = "GCL", project = "EWA")

```


### Get the most recent conditions at the [Fremont Bridge](https://en.wikipedia.org/wiki/Fremont_Bridge_(Seattle)) (station FBLW) in the [Lake Washington Ship Canal](https://en.wikipedia.org/wiki/Lake_Washington_Ship_Canal) (project LKW):

```{r Example Fremont Bridge}
library(acewater)

get_water_conditions(station = "FBLW", project = "LKW")
```


### Get Conditions from Multiple Stations

We can use [purrr](http://purrr.tidyverse.org) to combine data from multiple stations into a tidy data frame.
Here, we'll get data from a few stations along the [Lake Washington Ship Canal](https://en.wikipedia.org/wiki/Lake_Washington_Ship_Canal).

```{r Example Multiple Stations, message=FALSE, warning = FALSE}
purrr::map_df(c("UBLW", "FBLW", "LLLW"), get_water_conditions, project = "LKW")

```


### Plot Water Conditions

We can easily plot the water conditions for a given station (if [ggplot2](http://ggplot2.tidyverse.org) is installed).
Here, we'll extend the prevous Fremont Bridge example:

```{r Example Plot Fremont Bridge}
library(acewater)
library(ggplot2)

autoplot(get_water_conditions(station = "FBLW", project = "LKW"))
```


## Data Subject to Revision

Because the data retrieved by acewater are preliminary and have not been verified or approved by the agencies collecting them, inaccuracies may be present due to instrument malfunctions or physical changes at the measurement site.


## Contributer Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.

